---
title: "Case Study 1"
author: "David Liu"
output:
  html_document: default
  pdf_document: default
---

```{r setup}
install.packages("forecast",repos = "http://cran.us.r-project.org")
library(forecast)
library(zoo)
```

## QUESTION 1: Identify time series components and plot the data.
### 1a. Create time series data set in R using the ts() function.
```{r}
sales.data <- read.csv("673_case1.csv")
sales.ts <- ts(sales.data$Sales, start=c(2015,1), end=c(2019,12), freq=12)
sales.ts
```

```{r}
sales.data
```

### 1b. Employ the plot() function to create a data plot with the historical data, provide it in your report, and explain what data patterns can be visualized in this plot. 
```{r}
plot(sales.ts, xlab="Year", ylab="Sales (millions $)", ylim=c(0,500), 
     main="World Wide Monthly Sales")
```

### 1c. Apply the Acf() function to identify possible time series components. Provide in the report the autocorrelation chart and explain the time series components existing in the historical data. 
```{r}
sales.acf <- Acf(sales.ts, lag.max = 12, main = "Autocorrelation for Sales")
```

## QUESTION 2. Use trailing MA for forecasting time series.
### 2a. Use the rollmean() function to develop three trailing MAs (apply the entire data set with no partitioning) for the window width of 2, 6, and 12, respectively. Present the R code for these MAs in your report.
```{r}
sales.rollmean_2 <- rollmean(sales.ts, k=2, align="right")
sales.rollmean_6 <- rollmean(sales.ts, k=6, align="right")
sales.rollmean_12 <- rollmean(sales.ts, k=12, align="right")

sales.rollmean_2
sales.rollmean_6
sales.rollmean_12
```

### 2b. Use the forecast() function to create a trailing MA forecast for each window width in 12 months of 2020, and present these forecasts in your report. 
```{r}
sales.rollmean_2.pred <- forecast(sales.rollmean_2, h=12, level = 0)
sales.rollmean_6.pred <- forecast(sales.rollmean_6, h=12, level = 0)
sales.rollmean_12.pred <- forecast(sales.rollmean_12, h=12, level = 0)

sales.trail_2 <- c(sales.rollmean_2.pred)
sales.trail_6 <- c(sales.rollmean_6.pred)
sales.trail_12 <- c(sales.rollmean_12.pred)

sales.trail_forecast <- cbind(sales.trail_2$mean, sales.trail_6$mean, sales.trail_12$mean)
sales.trail_forecast
```

### 2c. Develop a seasonal naïve forecast for the entire historical data set, and apply the accuracy() function to compare accuracy of the four models: seasonal naïve forecast and trailing MAs with window width of 2, 6, and 12, respectively. Present the accuracy measures in your report, compare MAPE and RMSE of these forecasts, and identify the best forecasting model.
```{r}
sales.snaive.pred <- snaive(sales.ts, h=12)

naive.measures <- accuracy(sales.snaive.pred)
MA_2.measures <- accuracy(sales.rollmean_2.pred)
MA_6.measures <- accuracy(sales.rollmean_6.pred)
MA_12.measures <- accuracy(sales.rollmean_12.pred)

models <- c("Naive","Trailing_MA_2","Trailing_MA_6","Trailing_MA_12")
RMSE <- c(naive.measures[2], MA_2.measures[2], MA_6.measures[2], MA_12.measures[2])
MAPE <- c(naive.measures[5], MA_2.measures[5], MA_6.measures[5], MA_12.measures[5])

accuracy_table <- cbind(models, RMSE, MAPE)

accuracy_table
```


## QUESTION 3. Apply the two-level forecast with regression and trailing MA for residuals.
### 3a.	To de-trend and de-seasonalize the historical data for the entire data set, develop using the tslm() function a regression model with linear trend and seasonality and forecast sales in 2020 with the forecast() function. Present and briefly explain the model in your report. 
```{r}
reg.lin.seas <- tslm(sales.ts ~ trend + season)
summary(reg.lin.seas)

reg.lin.seas.pred <- forecast(reg.lin.seas, h = 12, level = 0)
reg.lin.seas.pred
```

### 3b.	Identify regression residuals, apply a trailing MA (window width of 2) for these residuals using the rollmean() function, and forecast worldwide monthly sales in 12 months of 2020 (use the forecast() function). Combine the regression and trailing MA residuals’ forecast for 2020, and present in your report a table that contains regression forecast, trailing MA forecast for residuals, and total (combined) forecast in 2020. 
```{r}
reg.lin.seas.residuals <- reg.lin.seas$residuals
reg.lin.seas.residuals
```
```{r}
trailing_MA.residual_2 <- rollmean(reg.lin.seas.residuals, k = 2, align = "right")
trailing_MA.residual_2

trailing_MA.residual_2.pred <- forecast(trailing_MA.residual_2, h = 12, level = 0)
trailing_MA.residual_2.pred
```
```{r}
combined_forecast <- reg.lin.seas.pred$mean + trailing_MA.residual_2.pred$mean
combined_forecast

dates <- c("Jan 2020","Feb 2020","Mar 2020","Apr 2020","May 2020","Jun 2020","Jul 2020","Aug 2020",
           "Sep 2020","Oct 2020","Nov 2020","Dec 2020")

total.pred <- data.frame(dates, reg.lin.seas.pred$mean, trailing_MA.residual_2.pred$mean, combined_forecast)
total.pred
```
### 3c.	Apply the accuracy() function to compare accuracy of the three forecasting models: seasonal naïve forecast (applied in question 2c), regression model with trend and seasonality, and two-level (combined) model with regression and trailing MA for residuals. Present the accuracy measures in your report, compare MAPE and RMSE of these forecasts, and identify the best forecasting model.
```{r}
naive.measures <- accuracy(sales.snaive.pred$fitted, sales.ts)
reg.lin.seas.measures <- accuracy(reg.lin.seas.pred$fitted, sales.ts)
combined_forecast.measures <- accuracy(reg.lin.seas.pred$fitted + trailing_MA.residual_2, sales.ts)

models <- c("Naive","lin reg with seasonality","two level model")
RMSE <- c(naive.measures[2], reg.lin.seas.measures[2], combined_forecast.measures[2])
MAPE <- c(naive.measures[5], reg.lin.seas.measures[5], combined_forecast.measures[5])

accuracy_table <- data.frame(models, RMSE, MAPE)

accuracy_table
```


## QUESTION 4. Use advanced exponential smoothing methods. 
### 4a.	Develop data partition with the validation partition of 12 historical periods and training partition of the rest of the historical periods. 
```{r}
validation <- 12
training <- length(sales.ts) - validation
sales_train.ts <- window(sales.ts, start = c(2015, 1), end = c(2015, training))
sales_valid.ts <- window(sales.ts, start = c(2015, training + 1), end = c(2015, training + validation))

sales_train.ts
sales_valid.ts
```

### 4b.	For the training partition, use the ets() function to develop a Holt-Winter’s model with multiplicative error, multiplicative trend, and multiplicative seasonality options, and automated selection of smoothing parameters for the training partition. Present and explain the model in your report. Use the model to forecast worldwide sales for the validation period using the forecast() function. 
```{r}
HW_model <- ets(sales_train.ts, model = "MMM")
HW_model

HW_model.pred <- forecast(HW_model, h = 12, level = 0)
HW_model.pred
```


### 4c.	To make a forecast for the 12 months of 2020, use the entire data set (no partitioning) to develop the Holt-Winter’s model using the ets() function with the automated selection of error, trend, and seasonality options, and automated selection of smoothing parameters. Present and explain the model in your report. Use the model to forecast worldwide sales for the 12 months of 2020 using the forecast() function. 
```{r}
HW_model_alldata <- ets(sales.ts)
HW_model_alldata

HW_model_alldata.pred <- forecast(HW_model_alldata, h = 12, level = 0)
HW_model_alldata.pred
```

### 4d.	Apply the accuracy() function to compare the two forecasting models: seasonal naïve forecast (applied in question 2c) and Holt-Winter’s model developed in question 4c. Present the accuracy measures in your report, compare MAPE and RMSE of these forecasts, and identify the best forecasting model. 
```{r}
naive.measures <- accuracy(sales.snaive.pred$fitted, sales.ts)
HW_model_alldata.measures <- accuracy(HW_model_alldata.pred$fitted, sales.ts)

models <- c("Naive","Holt-Winter's")
RMSE <- c(naive.measures[2], HW_model_alldata.measures[2])
MAPE <- c(naive.measures[5], HW_model_alldata.measures[5])

accuracy_table <- data.frame(models, RMSE, MAPE)

accuracy_table
```

### 4e.	Compare the best forecasts identified in questions 3c and 4c. Explain what your final choice of the forecasting model in this case will be.
```{r}
models <- c("Two Level Model","Holt-Winter's")
RMSE <- c(combined_forecast.measures[2], HW_model_alldata.measures[2])
MAPE <- c(combined_forecast.measures[5], HW_model_alldata.measures[5])

accuracy_table <- data.frame(models, RMSE, MAPE)

accuracy_table
```



